Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-03-06 chapters/final_remarks.tex
Changes 1. Completed conclusion except for aim 3

In Aim 1, bijels stabilized with spherical particles do not respond to the application of a magnetic field. However, bijels stabilized
with ellipsoidal particles have an increase in the average domain size by 3 \%. The microstructure also becomes anisotropic, 
characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
interface. The curvature also becomes more negative as the applied field strength is increased. The microstructure anisotropy is caused
by direction specific jamming of the particle monolayer originating from particle ordering to the magnetic field.

When investigating the particle monolayer, the orientational order changes as a function of the applied field strength and has particle
morphology specific time evolution. The interface angle was also characterized and shown to have magnetic field dependence, although
this was attributed to the orientational ordering of the particles on the interface. When analyzing the ordering of particles on the
interface, disc-like particles see lowered local ordering as the magnetic field strength is increased while rod-like particles see
greater local ordering. These properties are attributed to how those particle morphologies prefer to orient themselves at interfaces
to one another, with disc like particles preferring to stack while rod like particles order side to side or end to end.

In Aim 2

In Aim 3

>>>>

In Aim 1, bijels stabilized with spherical particles do not respond to the application of a magnetic field. However, bijels stabilized
with ellipsoidal particles have an increase in the average domain size by 3 \%. The microstructure also becomes anisotropic, 
characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
interface. The response characterized was particle morphology specific due to the orientation of the particle magnetic moment with 
respect to the direction of the long axis of the particle. This causes the particles to arrange differently on the interface. The 
microstructure anisotropy is caused by direction specific jamming of the particle monolayer originating from particle ordering to 
the magnetic field. The direction specific jamming originates from the orientation of the particles to the magnetic field. The direction
specific jamming also reduces the local curvature of the system as the interface location moves with the particle.

To investigate the role of the particle monolayer in greater detail, we characterize the orientational order to the magnetic field,
angle to the interface and local particle ordering at the interface. The orientational order changes as a function of the applied field 
strength and has particle morphology specific time evolution. When investigating the average interfacial angle of the particles to the 
interface, it is shown how the capillary interactions with the interface differ, leading to the time evolution differences observed.
When analyzing the ordering of particles on the interface, disc-like particles see lowered local ordering as the magnetic field strength is 
increased while rod-like particles see greater local ordering. These properties are attributed to how those particle morphologies prefer 
to orient themselves at interfaces to one another, with disc like particles preferring to stack while rod like particles order side to side 
or end to end.

In Aim 2, bijels stabilized by ellipsoidal particles demonstrate responses to an applied magnetic field. When applying a magnetic field
onto a bijel template simulated with no magnetic fields, we see an average microstructure change of up to 5 \%. This microstructure change
arises from the magnetic field driven re-orientation of particles at the interface. Particle reorientation creates microstructure anisotropy
arising from the alignment of particles to the magnetic field. When analyzing the particle monolayer, we characterize the alignment of particles
to the field direction, average interface angle and the local ordering of the particles. We demonstrate that the average interface angle increases
as the particles reorient to the field before the capillary forces of the interfaces causes the interface to move, until jamming of the monolayer takes
place. The local particle order during this process decreases for oblate particles and increases for prolate particles. We characterize that the local 
order of the particles controls the timescales of response.

When investigating the effect of pre-existing order of the particle monolayer, we show that the structural response of the bijel is dependent upon the
difference between the field applied to make the bijel and the applied field when the field is applied in the same direction. We also characterize that the
local particle monolayer is dependent upon the pre-existing order of the bijel. When switching off the magnetic field onto bijels made with a magnetic field,
we see that the microstructure remains resilient to the removal of the magnetic field. We characterize that while there are differences in the particle monolayer,
these differences manifest as when domain coarsening begins. When characterizing the hysteresis curve of the bijels stabilized with prolate particles,
we see the effect of this.

In Aim 3 we investigate the rheological response of bijels stabilized with ellipsoidal particles under constant shear and show that the application of magnetic
fields changes the shear thinning properties of bijels.
